\documentclass[sigconf]{acmart}


\usepackage{graphicx}
%\usepackage[draft]{graphicx}
\usepackage{subcaption}


\usepackage{booktabs} % For formal tables

\usepackage{bibnames}
\usepackage[T1]{fontenc}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage{paralist} % for inline lists
%\usepackage[allfiguresdraft]{draftfigure}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{lipsum}

\usepackage[capitalise,nameinlink]{cleveref}
\def\tightlist{}

\usepackage{import}
\newcommand{\smallunderscore}{\textscale{.5}{\textunderscore}}
\renewcommand{\_}{\textscale{.5}{\textunderscore}}

% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{xx.xxx/xxx_x}

% ISBN
\acmISBN{979-8-4007-0629-5/25/03}

%Conference
\acmConference[SAC'25]{ACM SAC Conference}{March 31 –April 4, 2025}{Sicily, Italy}
\acmYear{2025}
\copyrightyear{2025}


\acmArticle{4}
\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}


\begin{document}
\title{Evaluation of Uncertainty Estimation in Deep learning using
Constraint-Based Dataset Generation}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}
  
\renewcommand{\shorttitle}{Uncertainty Evaluation}


\author{Deebul Nair}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{SpaceR Research Group }
  \streetaddress{University of Luxembourg}
  %\city{Dublin} 
  %\state{Ohio} 
  \country{Luxembourg}
 % \postcode{43017-6221}  
}
%\email{trovato@corporation.com}

\author{Sathwik Panchangam}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Artificial Intelligence and Autonomous Systems }
  \streetaddress{Hochschule Bonn-Rhein-Sieg}
  %\city{Dublin} 
  %\state{Ohio} 
  \country{Germany}
 % \postcode{43017-6221}  
}
%\email{trovato@corporation.com}

\author{Miguel A. Olivares-Mendez}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{SpaceR Research Group }
  \streetaddress{University of Luxembourg}
  %\city{Dublin} 
  %\state{Ohio} 
  \country{Luxembourg}
 % \postcode{43017-6221}  
}
%\email{trovato@corporation.com}

\author{Nico Hochgeschwender}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{ Department of Mathematics and Computer Science }
  \streetaddress{University of Bremen}
  %\city{Dublin} 
  %\state{Ohio} 
  \country{Germany}
 % \postcode{43017-6221}  
}
%\email{trovato@corporation.com}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Nair. D et al.}


\begin{abstract}
{Uncertainty estimation in deep learning methods is a challenging problem
because there is no true label available for uncertainty. Evaluation of the uncertainty estimation
methods is a critical component for determining their practical utility,
particularly when making decisions based on the predictions generated by
a model.}
{This paper identifies the shortcomings of existing techniques for assessing uncertainty estimation methods especially for embodied agent applications. To overcome these limitations, we introduce constraint-based dataset generation.}
{Our methodology allows us to systematically evaluate the performance of
different uncertainty estimation methods in a controlled and
reproducible simulated environment. We generate subset of the datasets for image
classification task based on constraints and then compare the predicted
uncertainties between these subsets based on expert knowledge.}
{We  evaluated three different
uncertainty estimation methods and reported on their differences.}
{The proposed methodology should help in better understanding the uncertainty estimation capability of deep learning models deployed in embodied agents.}

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10010520.10010575.10010577</concept_id>
       <concept_desc>Computer systems organization~Reliability</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10010147.10010341.10010342.10010345</concept_id>
       <concept_desc>Computing methodologies~Uncertainty quantification</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10010147.10010257.10010293.10010294</concept_id>
       <concept_desc>Computing methodologies~Neural networks</concept_desc>
       <concept_significance>100</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Reliability}
\ccsdesc[500]{Computing methodologies~Uncertainty quantification}
\ccsdesc[100]{Computing methodologies~Neural networks}

\keywords{Uncertainty estimation, synthetic dataset generation, DNN}


\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{demo.bib}

\end{document}
